Appendix A : Dipole-dipole interaction between two spins in solid

### 2022-07-26 Manuscrit Thèse/chapter 2/Chapter 2.tex
tata

While both cross-relaxation and DEER measure the dipole-dipole coupling of dark spins to an NV center, there are several differences between the two protocols :

>>>>

While both cross-relaxation and DEER measure the dipole-dipole coupling of dark spins to an NV center, there are several differences between the two protocols:
